Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-28 paper/main.tex
imA

The graphic category $\mathcal{\gtotal}$ consists of the functor object $\sheaf_{\gtotal}: \mathcal{S}^{op} \rightarrow \Gamma(\mathcal{S}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{S}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{S}, \gtotal)$ is a subcatagory of \texbf{Set}. A set $\Gamma(U_i, \gtotal)$ contains functions to generate arbitrary graphics with a shared continuity and display space, while the artist $\vartist$ is constructed such that it generates a single type of graphic, as described in \autoref{sec:artist:construction}. Therefore, the range of the the artist functor, which we denote $Im_{\vartist}$, is a sheaf map $Im_{\vartist}$. The sheaf $Im_{\vartist}$ is a map between the category of open sets $\gtotal^{op}$ and a subcategory of \textbf{Set}. In this subcatagory, each set of sections in the sheaf $Im_{\vartist}$ over an arbitrary open set $U_{i}$ is a subset of the corresponding full set of sections $\Gamma(U_i, \gtotal)$.

Since the artist is a morphism of sheafs
\begin{equation}
  \vartist: \mathcal{\dtotal} \rightarrow Im_{\vartist}
\end{equation}
it is by definition a natural transformation\cite{SheafMathematics2021,bradleyWhatNaturalTransformation}. This means that all morphisms $\varphi$ on $\mathcal{\dtotal}$ are expected to commute \cite{spanier1989algebraic,fongInvitationAppliedCategory2019}. This is the basis of the equivariance condition illustrated in \autoref{eq:artist:equivariance}

@@

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vartist_a"] &  &             &  & {\Gamma(\gbase_a, \gfiber_a)} \arrow[lld, "g_a" description, dashed] \\
                                                                           &  & \dfiber_{c} &  &                                                                      \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vartist_b"] &  &             &  & {\Gamma(\gbase_a, \gfiber_a)} \arrow[llu, "g_b" description, dashed]
\end{tikzcd}
\end{equation}

@@

\subsection{Graphic} 
The object of the graphic category $\mathcal{\gtotal}$ is the fiberbundle \gtotal. The bundle \gtotal\ has the same structure as the data bundle \dtotal

>>>>

The graphic category $\mathcal{\gtotal}$ consists of the functor object $\sheaf_{\gtotal}: \mathcal{S}^{op} \rightarrow \Gamma(\mathcal{S}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{S}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{S}, \gtotal)$ is a subcatagory of \texbf{Set}.

\begin{definition} The sheaf $Im_{\vartist}$ is a map between the category of open sets $\gtotal^{op}$ and a subcategory of \textbf{Set}. This subcategory is the set of subsets of sections $\{\gsection^{k}:U_i \rightarrow \gfiber_{U_{i}}\} \subset \Gamma(U_i, \gtotal)$ over the space of all open sets in $\mathcal{\gbase}$. 
\end{definition}

A set $\Gamma(U_i, \gtotal)$ contains functions to generate arbitrary graphics with a shared continuity and display space, while the artist $\vartist$ is constructed such that it generates a single type of graphic, as described in \autoref{sec:artist:construction}. Therefore, the range of the the artist functor, which we denote $Im_{\vartist}$, is a sheaf map $Im_{\vartist}$. Since the artist is a morphism of sheafs
\begin{equation}
  \vartist: \mathcal{\dtotal} \rightarrow Im_{\vartist}
\end{equation}
it is by definition a natural transformation\cite{SheafMathematics2021,bradleyWhatNaturalTransformation}. This means that all morphisms $\varphi$ on $\mathcal{\dtotal}$ are expected to commute \cite{spanier1989algebraic,fongInvitationAppliedCategory2019}. This is the basis of the equivariance condition illustrated in \autoref{eq:artist:equivariance}

@@

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vartist_a"] &  &             &  & {\Gamma(\gbase_a, \gfiber_a)} \arrow[lld, "g_a" description, dashed] \\
                                                                           &  & \dfiber_{c} &  &                                                                      \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vartist_b"] &  &             &  & Im_{\vartist_b} \in \gtotal \arrow[llu, "g_b" description, dashed]
\end{tikzcd}
\end{equation}

@@

\subsection{Graphic} 
The object of the graphic category $\mathcal{\gtotal}$ is the fiber bundle \gtotal. The bundle \gtotal\ has the same structure as the data bundle \dtotal
